### 2015-07-10 narrative/intro.tex

Central to our approach is giving users the ability to define the utility of their data    
 \S\ref{sec:data-description}.
This includes the ability to assign varying levels of importance to individual data objects in their entirety, or to specific
subsets and pieces.
Key research challenges include: 1) developing an expressive and easy to use program interface, 2) formulating a system model that can support 
autonomic decision, for example, for saving data based on user-defined importance and utility of data~\S~\ref{sec:managing-data-life}),
 and 3) the interface between the system and the back-end storage across both single, and multiple running applications~\S~\ref{sec:qos}.

 %
  In our  scenario we would like the scientist would then specify a set of rules that governed the actual behavior while the simulation is running.
If the system resources are available and the estimated write times are in order, the write can proceed.
%Or, the write can be postponed to a later time-step, or data reduced via in situ techniques can be saved.
Data  utility will be used to place the various data on the proper SSIO layer.
The user specified lifetime for each data ensures that the data with the highest utility is preserved in fast storage
for the longest period of time, and the least utility are migrated to lower storage  layers.
%
%Since the data will be a collection of objects placed on the storage system,
%some of the objects will be broken up into multiple pieces by ``plug-ins''
%to the system which will allow data to be characterized first in terms of the most
%important pieces, and then by subsequent levels of detail. We can think of this as
%something similar to an Adaptive Mesh Refinement scheme which keeps track of
%the places where there are features such as steep gradients, which contain large errors on the
%coarser views, as opposed to other areas with smaller errors. These distinctions allow us to make decisions
%about which sub-objects to save (all of the data, which will then go to
%different layers) or just some of the sub-objects? The research questions
%are numerous: How does the user specify their intentions? How does the user
%prioritize the different sub-objects of the data? Where does the data go
%into the storage hierarchy? Does the data get replicated in the lower tiers
%of the hierarchy? When the user specifies the time they want the data saved,
%how does this get into the storage system?

>>>>

Central to our approach is giving users the ability to define the utility of their data    
 \S\ref{sec:data-description}.
This includes the ability to assign varying levels of importance to individual data objects in their entirety, or to specific
subsets and pieces.
Key research challenges include: 1) developing an expressive and easy to use a program interface, 2) formulating a system model that can support 
autonomic decision, for example, for saving data based on user-defined importance and utility of data~\S~\ref{sec:managing-data-life}),
, and 3) defining the interface between the system and the back-end storage for both single and multiple running applications~\S~\ref{sec:qos}.

In the scenario above, the scientist would then specify a set of rules that would guide I/O and data management 
at runtime. For example, if system resources are available and the estimated write times acceptable, the write 
can proceed, but if this is not the case, the write may be postponed to a later time-step, or the data reduced using
an in-situ techniques before it is saved. Data ``importance or utility'' can be used to place various data at  
proper SSIO layers -- data with the highest utility (e.g., based on user defined importance or the frequency of access) 
is maintained in faster storage for long periods of time, while data with lower utility can be migrated to lower layers 
in the storage hierarchy.

%
%Since the data will be a collection of objects placed on the storage system,
%some of the objects will be broken up into multiple pieces by ``plug-ins''
%to the system which will allow data to be characterized first in terms of the most
%important pieces, and then by subsequent levels of detail. We can think of this as
%something similar to an Adaptive Mesh Refinement scheme which keeps track of
%the places where there are features such as steep gradients, which contain large errors on the
%coarser views, as opposed to other areas with smaller errors. These distinctions allow us to make decisions
%about which sub-objects to save (all of the data, which will then go to
%different layers) or just some of the sub-objects? The research questions
%are numerous: How does the user specify their intentions? How does the user
%prioritize the different sub-objects of the data? Where does the data go
%into the storage hierarchy? Does the data get replicated in the lower tiers
%of the hierarchy? When the user specifies the time they want the data saved,
%how does this get into the storage system?
